---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%", 
  fig.width=10, 
  dpi=300
)
```

# Voronoise

<!-- badges: start -->
<!-- badges: end -->

The goal of voronoise is to make pretty pictures. It is a very minor tweak on the voronoi tesselations provided by the `ggforce` package. You can install the development version of voronoise from GitHub with:

``` r
remotes::install_github("djnavarro/voronoise")
```

## Example

Create a tibble with columns specifying the x and y coordinates, and the colours to be associated with the corresponding Voronoi cell

```{r dataset}
library(voronoise)

set.seed(1)

dat <- tibble::tibble(
  x = runif(n = 50, min = .1, max = .9),
  y = runif(n = 50, min = .1, max = .9),
  shade = sample(colours(), size = 50, replace = TRUE)
)

dat
```

The `voronoise_base()` function initialises a ggplot object

```{r}
voronoise_base(dat)
```

The default behaviour of `geom_voronoise()` is identical to `ggforce::geom_voronoi_tile()` with some parameter values changed. It does not perturb the location of any of the tiles:

```{r boring}
voronoise_base(dat) + 
  geom_voronoise(fill = "antiquewhite2")
```

To perturb the tiles we need to pass it a `perturb` function:

```{r uniform}
voronoise_base(dat) + 
  geom_voronoise(fill = "antiquewhite2") + 
  geom_voronoise(perturb = perturb_uniform(.2))  
```

Note that `perturb_uniform()` returns a function. The voronoise package comes with a couple of handy functions that will create custom perturbing functions. For example:

```{r}
voronoise_base(dat) + 
  geom_voronoise(fill = "antiquewhite2") + 
  geom_voronoise(perturb = perturb_float(-90))
```

An example using some more settings:

```{r}
set.seed(1)
voronoise_base(
  data = voronoise_data(100, viridis::magma(10)), 
  background = "skyblue3"
) + 
  geom_voronoise(fill = "skyblue2") + 
  geom_voronoise(
    perturb = perturb_float(
      angles = c(0, 90, 180), 
      noise = c(2, 1)
    )
  )
```




